\documentclass[aspectratio=169]{beamer}

% generic packages

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{abraces}

% about the presentation
\title{Resource Directory}
\subtitle{\texttt{draft-ietf-core-resource-directory}}
\author{\textit{Christian~Amsüss}, Zach Shelby, Michael Koster, Carsten Bormann, Peter~van~der~Stok}
\date{2020-11-17}

% used commands

\usepackage{verbatim}

% attach self

\usepackage{embedfile}
\embedfile{\jobname.tex}

\begin{document}

\frame{\titlepage}

\begin{frame}{Since IETF108}\Large
	\framesubtitle{Processing IESG review}

	Picking highlights here; full changelog is detailed.

	\bigskip

	\begin{itemize}
		\item “First Come First Remembered”: example policy; implementatons may choose as default
		\item Host discovery {\em is not} secured, path discovery {\em is} if needed
		\item Move simple registration from \texttt{/.well-known/core} to \texttt{/.well-known/rd}
		\item More care for \texttt{rt} registered values
	\end{itemize}
\end{frame}

\begin{frame}{But treating them raised questions}\Large
	“When DTLS is used like TLS, replay protection should be considered”

	\bigskip

	\begin{tabular}{lll}
		Event & Reqeust & Response \\ \hline
		Power on & \texttt{POST /rd?ep=node1} & \texttt{/reg/reg1} \\
		Power off & \texttt{DELETE /reg/1}\footnote{sniff sniff} & Deleted\\
		Power on & \texttt{POST /rd?ep=node1} & \texttt{/reg/reg1} \\
		Replayed message & \texttt{DELETE /reg/1} & on but gone \\
	\end{tabular}

	\bigskip

	Works with and without replay protection, even in OSCORE
\end{frame}

\begin{frame}{Step to be taken}\Large
	Server ensures freshness using Echo.

	\bigskip

	Mechanism already referenced for Simple Registration and amplification mitigation.

	\bigskip

	WIP text is in \href{https://github.com/core-wg/resource-directory/pull/291}{\#291}\footnote{See there for explored alternatives.}.
\end{frame}

\begin{frame}{Server authorization}\Large
	Q: “How much can you trust links from the RD?”

	\bigskip

	A: “As far as this is allowed by security policies.”

	\vspace{1cm}
	\pause
	\hrule
	\vspace{1cm}

	\onslide<2>{
	$\textsf{Intention} \qquad\rightarrow\qquad \textsf{Request} \qquad\rightarrow\qquad \textsf{Effect / Response}$
	}
	\pause
	\vspace{-1cm}

	$\textsf{Create a topic} \quad\aoverbrace[]{\rightarrow}^{\texttt{rt=topics}}\quad \underbrace{\texttt{POST /tpcs} \quad\rightarrow\quad \textsf{Topic gets created}}_{\textsf{security layers}}$

	\bigskip

	Trust an authorized RD that checks, or verify before use.

	\bigskip

	\footnotesize And this can be way more powerful with forms, or when the RS sets the ACE scope.
\end{frame}

\begin{frame}{Possibilities to be explored}\Large
	\framesubtitle{on the long term -- outside RD}

	\begin{itemize}
		\item Single-use servers: “If it's on this host, it's the PubSub server.”

			Security contexts multiply.

			\bigskip

		\item Deposited verifiable statments in the RD.

			Granularity? Audience?

			\bigskip

		\item Finer grained authorization: “\ldots is authorized to provide the PubSub service at its \texttt{/tpcs} resource.”

			Linking to requests without multiplying contexts?
	\end{itemize}
\end{frame}

\begin{frame}{And by the way, your examples are needlessly large}\Large

	Yes. RFC6690, ambiguity, different readings\ldots

	\bigskip
	\pause

	\ldots but turned out mine was the worst.

	\bigskip

	\begin{itemize}
		\item In many resource lookup results, \texttt{anchor} is superfluous.
		\item TBD: Give precise rules when anchor must still be set, \\ rewrite examples.
		\item Existing RD servers stay compliant (just verbose).
		\item Pending recheck of the RFC6690 implementations.
	\end{itemize}
\end{frame}

\begin{frame}{Outlook}\Large
	\texttt{-27} around start of December:

	\bigskip

	Freshness on registration updates.

	\bigskip

	Relaxed anchor setting.

	\bigskip

	Continued exploration of protecting intention?
\end{frame}

\end{document}
