\documentclass[aspectratio=169]{beamer}

% generic packages

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% about the presentation
\title{Resource Directory}
\subtitle{\texttt{draft-ietf-core-resource-directory}}
\author{Zach Shelby, Michael Koster, Carsten Bormann, Peter~van~der~Stok, \textit{Christian~Amsüss}}
\date{2020-04-16}

% used commands

\usepackage{verbatim}

% attach self

\usepackage{embedfile}
\embedfile{\jobname.tex}

\begin{document}

\frame{\titlepage}

\begin{frame}{Status}\Large
	\texttt{-24} processed IETF016 comments

	\bigskip

	{\normalsize\begin{itemize}
		\item discovery via DNS-SD included explicitly for CoAP[S] over UDP and TCP
		\item lifetime minimum 60 → 1
		\item Explicit statement on anchor as lookup attribute
		\item IANA, references, examples, layout
	\end{itemize}}

	\bigskip

	Secdir: ready

	Genart: not read

	→ Revised I-D Needed
\end{frame}

\begin{frame}{Easy points}\Large
	\begin{itemize}
		\item Example errors
		\item Language consistency
		\item Dots and dashes
	\end{itemize}

	\bigskip

	Text ready in PRs or will be soon
\end{frame}

\begin{frame}{Needs a bit of thought}\Large
	\begin{itemize}
		\item DDOS mitigation. Non-normatively mention recommendation-to-come for Echo in ERT?
		\item Simple registration from fake sender as firewall bypass. Require client aliveness? When?
		\item Random endpoint names picked by client. Guidance on size might suffice, but is it thought through?
	\end{itemize}
\end{frame}

\begin{frame}{Input would help -- who knows X.509?}\Large
	\begin{itemize}
		\item {\texttt the certificate is uniquely identified by the CN field and the serial number}
		\item What in a certificate {\em can} be used?
		\item And how is it properly referenced?
	\end{itemize}
\end{frame}

\end{document}
